Scaling continuous reinforcement learning up

### 2018-11-08 paper/main.tex

\newcommand{\deltat}{{\delta t}}
\newcommand{\gauss}{\mathcal{N}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\TODO}[1]{\textcolor{red}{#1}}
\newcommand{\bigO}[1]{O(#1)}
\newcommand{\Tdo}{TD($0$)}

@@

>>>>

\newcommand{\deltat}{{\delta t}}
\newcommand{\gauss}{\mathcal{N}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\TODO}[1]{\textcolor{red}{#1}}
\newcommand{\bigO}[1]{O(#1)}
\newcommand{\Tdo}{TD($0$)}
\newcommand{\tdres}{\delta_\text{TD}}

@@

\paragraph{Resulting update equations}
The resulting update equations on $\theta$, $\phi$ and $b$, for a transition
quadruplet $(s, a, s', \tilde{r}(s, a))$ and a state $s''$ independant from the
quadruplet are
\begin{align}
	\tdres &= A_\theta(s, a) - 
	\max\limits_{a'} A_\theta(s, a')-
	\tilde{r}(s, a) + b - \frac{\gamma^\deltat V_\phi(s') - V_\phi(s)}{\deltat}\\
	\delta \theta &= \deltat \left(\alpha_1 \tdres \partial_\theta \left(A_\theta(s, a) - 
		\max\limits_{a'} A_\theta(s, a')\right)
	+ \alpha_2 \max\limits_{a'} A_\theta(s, a')\partial_\theta \max\limits_{a'} A_\theta(s, a')\right)\\
	\delta \phi &= \deltat \left( \alpha_3 \tdres \partial_\phi V_\phi(s) + \alpha_4 V_\phi(s'')\partial_\phi V_\phi(s)\right)\\
	\delta b &= \deltat \alpha_5 \tdres\\
	\theta &\leftarrow \theta - \delta \theta\\
	\phi &\leftarrow \phi - \delta \phi\\
	b &\leftarrow b - \delta b\\
\end{align}

\paragraph{Alternate update rule for $b$}
Averaging advantage updating bellman equation over the stationary distribution of the current policy $\pi$, $b$ can be shown to verify
\begin{equation}
	b = \E_{(s, a) \sim \rho^\pi \times \pi}\left[\tilde{r}(s, a) - A^*(s, a)\right]
\end{equation}
yielding a different update rule for $b$
\begin{equation}
	b \leftarrow (1 - \alpha_5 \deltat) b + \alpha_5 \deltat \left(\tilde{r}(s, a) - A^*(s, a)\right).
\end{equation}
